Analysis Stand Features 

### 2018-01-22 analysis/analysis_stand_features.Rmd
update

---
title: "Analysis Stand Features "
author: "AJ Perez-Luque (@ajpelu)"
date: "2018 Jan"
output:   
  md_document:
    toc: true
    variant: markdown_github
---

>>>>

---
title: "Analysis Stand Features "
author: "AJ Perez-Luque (@ajpelu)"
date: "2018 Jan"
output:  
  md_document:
    toc: true
    variant: markdown_github
bibliography: references.bib 
csl: ecology.csl
---
